
1. High Abstraction in JavaScript

    1. We don't have to handle resource managemnet and memory allocation
    2. We don't have to handle garbage collection
    3.Reduces details so that developers can focus on logic better
    4. Imroves understandblility as well as maintainabilit of the code. 

2. Garbage Collection in JavaScript

    1. JavaScript automatically collects unused data. 
    2. Free the memory with the help of an algorithm called 'Mark-and-sweep'
    3. The garbage collector goes through the roots marking (remembering) them on its way. 
    4. It then moves on to the references and marks them as well. 
    5. The cycle continues until the garbage collector visits all the roots and references. 
    6. The garbage collector removes all the objects except the marked ones.

3. JavaScript is a JIT compiled language

    1.  JavaScript is not a purely interpreted language .
    2. Modern JavaScript is JIT compiled. 
    3. JUST-IN-TIME compiler converts the entire code into machine code and execute them immediately. 

4. JavaScript is a multi-paradigm programming language.

    1. Procedural programming
    2. Object-Oriented programming
    3. Functional Programming 

5. JavaScript is a proto-typed based programming language.

    1. In JavaScript, everything(function array object) is object except the primitive data.
    2. a prototypical object is an object used as a template from which to get the initial properties for a new object.
    3. Proto-type is a blue print.

6. JavaScript is dynamically typed programming language.

    1. When you declare a variable, you do not need to specify what type this variable is. 
    2. JavaScript engine infers what type this variable is based on the value assigned to at run time.
    3. As JavaScript determines the type at runtime we can re-declare the type;